Web Scraping

### 2022-03-03 manuscript_version/web_scraping.Rmd
update for tables why do they hate me

---
title             : "Moral Foundations of U.S. Political News Organizations"
shorttitle        : "MORAL NEWS"

author: 
  - name          : "William E. Padfield"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "901 S. National Ave, Springfield, MO, 65897"
    email         : "Padfield94@live.missouristate.edu"
  - name          : "Erin M. Buchanan, Ph.D."
    affiliation   : "2"
  - name          : "Kayla N. Jordan, Ph.D."
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Missouri State University"
  - id            : "2"
    institution  : "Harrisburg University of Science and Technology"

author_note: |
  William Padfield is a master's degree candidate in Psychology at Missouri State University. This thesis partially fulfills the requirements for the Master of Science degree in Psychology.

abstract: |
  Partisan differences and diviseness have become an increasing hot topic in psychological research. Many theories have been proposed to explain these differences and divisions including Moral Foundations Theory. The current research seeks to use a linguistic measure of Moral Foundations, the Moral Foundations Dictionary (MFD), to test the theory in terms of predicted partisan differences. Through web scraping, the researchers extracted articles from popular partisan news sources' websites, calculated MFD word frequencies, and identified words' respective valences. This process attempts to uncover news outlets' positive or negative endorsements of certain moral dimensions concomitant with a particular ideology. In Experiment 1, the researchers gathered political articles from four sources. We were unable to reveal significant differences in moral endorsements, but we solidified the method to be employed in further research. In Experiment 2, the researchers expanded their number of sources to 10 and analyzed articles that pertain to two specific topics: the 2018 confirmation hearings of U.S. Supreme Court Justice Brett Kavanaugh and the partial U.S. Government Shutdown of 2018-2019. Once again, no significant differences in moral endorsements were found. Together with past work, the results shed doubt on the validity of the MFD as a measure.

keywords          : "politics, morality, psycholinguistics"

bibliography      : ["metapsych_bib.bib"] #turn this off right now so it knits

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
replace_ampersands: yes
csl               : apa6.csl
---

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)

knitr::opts_chunk$set(cache = TRUE)
options(tinytex.verbose = TRUE)
```

The field of moral psychology has a long history with modern moral psychology beginning in the late 1960s with Lawrence Kohlberg's theory of moral development [@Kohlberg1977].Since then, Kohlberg's theory has been highly criticized with numerous theory and hypotheses being proposed to replace it. One of these theories is Moral Foundations Theory (MFT) proposed by Jonathan Haidt and Jesse Graham [@Haidt2007]. While the theory itself has been widely criticized and debated, the goal of the current work is to tackle a related issue, the Moral Foundations Dictionary (MFD) [@Graham2009].@Graham2009 developed a lexicon-based linguistic measure of MFT arguing that moral concerns and the propositions of MFT could be measured and tested with the words people use. Here we first review evidence and criticisms against this assumption. We then provide our own test of the MFD using partisan news articles.

## Moral Foundations Dictionary

Jonathan Haidt and Jesse Graham formulated Moral Foundations Theory as a method by which to capture the entirety of humans' moral domain [@Haidt2007]. The researchers argued older theories of moral psychology were focused primarily on issues of justice, fairness, and caring - individually focused foundations of morality that align with the beliefs of political liberals [@Haidt2007]. In other words, moral psychology ignored the valid moral foundations of conservatives. Moral Foundations Theory (MFT) holds that people's moral domain can be mapped by quantifying their endorsement of five moral foundations: *harm/care*, *fairness/reciprocity*, *ingroup/loyalty*, *authority/respect*, and *purity/sanctity* [@Haidt2007].

In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text. The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations. @Graham2009 created a preliminary list of words that they believed would be associated with the five foundations. Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list.

Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers. Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers. However, conservative ministers did not use *ingroup/loyalty* words more than liberals. Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].

## Critiques of Moral Foundations

Moral Foundations Theory has received criticism on the grounds that its assumptions regarding moral intuitions have little empirical basis. @Suhler2011 criticized the content and taxonomy of the five foundations and question whether or not the foundations are sufficiently distinct as to stand as their own foundation. Likewise, @Gray2015 argues that the measurement of the moral foundations confounds morality with other constructs (such as weirdness) and the moral foundations lack statistical and conceptual distinction. @Schien2015 argues that harm-based morality is the most parsimonious and logical explanation for MFT findings.

Beyond the critiques of the theory itself, many have also provided strong critiques of the Moral Foundations Dictionary (MFD).Conducting two close conceptual replication and six extension studies, @Frimer2020 found that the liberal-conservative differences found in the original study replicated in only 30% of cases and the effect sizes were over 30 times smaller than reported in @Graham2009.In a meta-analysis, the theorized differences were only found for authority and purity (e.g. conservatives used more authority and purity word). Loyalty was contrary to theoretical predictions (e.g. used more by liberals), and no differences were found for harm and fairness.Other studies have also found conflicting findings which fail to support the basic assertions of MFT. Exploring the political Twitterverse, @Sterling2018 found differences in the MFD to depend on political sophistication. For example, harm words were used more by liberals only if they had low levels of political sophistication; at high levels of political sophistication, conservatives used more harm words. While the MFD has not been extensive used (at least in published research), studies which have use the MFD to test partisan differences have found mixed results in terms of supporting MFT [@Clifford2013; @Frimer2015; @Sagi2014].

The most successful attempts to validate a linguistic measure of moral foundations have used more complex methods (compared to the original dictionary-based approach).These attempts generally fall into two categories: human annotations and semantic representations. @Hopp2021 represents the first approach where instead of relying on 'experts', a large sample of lay people were crowdsourced to manually annotate document for content relevant to each foundation. While resource-intensive, this method better captures how people may encounter and judge moral issues in everyday life leading to a more ecologically valid dictionary. @Garten2016 represents the second categories which instead relies on data-driven semantic analysis. Using shallow learning models like word2vec, moral foundations are measured using semantic similarity vectors rather than simple word counts.

As a further conceptual replication of @Frimer2020, here we test the liberal-conservative difference proposed by MFT using partisan media content and the Moral Foundations Dictionary. We first test differences in a general news corpus compared liberal sources (NPR and New York Times) to conservative sources (Fox News and Breitbart). Second, we examined news about specific political events: Brett Kavaugh's Supreme Court nomination and the Government Shutdown in 2018-19. Here the news sources were expanded to cover NYT, NPR, Slate, Huffington Post, and Politico on the liberal side and Fox News, Breitbart, The Rush Limbaugh Show, The Blaze, and Sean Hannity on the conservative side. To address potential issues of measurement with the MFD, the MFD was combined with previous research by the current authors (see below) and weighted by valence to create weighted percentages to better specify endorsement. Like @Frimer2020, results were judged based on the direction of the liberal-conservative difference compared MFT predictions and the size of the effect compared to past studies.

# Experiment 1

# Method

For Experiment 1, the researchers approached the study with the intention to answer a method question. That is, this portion of the current research was conducted in order to solidify the best method by which to analyze political news text under the Moral Foundations Theory framework while also alleviating some of the aforementioned valence problem observed in the Moral Foundations Dictionary. The researchers hypothesized the news sources generally perceived as liberal leaning (*NPR* and *The New York Times*) would contain MFD words and valences indicating endorsements of the individualizing moral foundations (*harm/care* and *fairness/reciprocity*). Additionally, the researchers hypothesized the two sources generally perceived to be conservative leaning (*Fox News* and *Breitbart*) would feature MFD words and valences indicating equal endorsement of all five foundations. Owing to the lack of a need for human participants, the researchers did not petition Missouri State University's Institutional Review Board, as no such approval was needed to conduct this study.

## Sources

Political articles were collected from the websites of four notable U.S. news sources, a process known as web scraping. The sources were *The New York Times*, *National Public Radio (NPR)*, *Fox News*, and *Breitbart*. They were selected for their widespread recognition and the fact political partisans have strong preferences for some sources over others. The researchers determined the political lean of each source by referencing @Mitchell2014's article demonstrating the self-reported ideological consistency represented by the consumers of several news sources. In general, *The New York Times* and *NPR* are preferred by consumers reporting a liberal bias or lean. In contrast, *Fox News* and *Breitbart* are believed to have a conservative bias or lean. @Mitchell2014's article presented political ideology as a scale ranging from "consistently liberal" to "consistently conservative." In between these extremes lie more moderate positions, including "mostly liberal," "mixed," and "mostly conservative." Owing to the lower number of sources analyzed herein, the researchers elected to categorize the sources as either "liberal" and "conservative" in order to form a basis for comparison.

Political articles in particular were identified and subsequently scraped by including the specific URL directing to each source's political content in the *R* script. For example, rather than scrape from nytimes.com, which would return undesired results (non-political features, reviews, etc.), we instead included nytimes.com/section/politics so that more or less exclusively political content was obtained. All code for this manuscript can be found at https://osf.io/5kpj7/, and the scripts are provided inline with this manuscript written with the *papaja* library [@Aust2017].

Identification of the sources' political URLs presented a problem for two of the sources owing to complications with how their particular sites were structured. While in the multi-week process of scraping articles, we noticed word counts for *NPR* and *Fox News* were not growing at a similar pace as those from *The New York Times* and *Breitbart*. Upon investigation, we found another, more robust URL for political content from NPR: their politics content "archive." The page structure on NPR's website was such that only a limited selection of articles is displayed to the user at a given time. Scraping both the archive and the normal politics page ensured we were obtaining most (if not all) new articles as they were published. We later ran a process in order to exclude any duplicate articles. *Fox News* presented a similar issue. We discovered *Fox News* utilized six URLs in addition to the regular politics page. These URLs led to pages containing content pertaining the U.S. Executive Branch, Senate, House of Representatives, Judicial Branch, foreign policy, and elections. Once again, duplicates were subsequently eliminated from any analyses.

## Materials

Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@Wickham2016]. Using this dataset, we identified word count and average word count per source. This process was completed once daily starting in February 2018 until March 2018. Starting in mid-March 2018, the process was completed twice daily - once in the morning and again in the evening. Data collection was terminated once 250,000 words per source was collected in April 2018.

@@

## Data analysis

Once data collection ended, the text was scanned using the *ngram* package in *R* [@Schmidt2017]. This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.

@@

The article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@Feinerer2017]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset. Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were matched to their respective valence value.

Concurrent research by @Jordan2019 is assessing the validity of both the Moral Foundations Questionnaire and the Moral Foundations Dictionary through a multi-trait multi-method analysis of the two instruments using multiple samples. The instruments and foundation areas are being analyzed against one another, in order to test reliability, as well as against the Congressional Record in order to test predictive validity for political orientation. The researchers were able to identify a number of potential new words that, if added to the MFD, could comprise a dictionary with greater validity, and less likelihood of zero percent texts, as this often occurs with the current MFD. Those results have informed this analysis, and their updated findings may change the underlying dictionary used in this analysis (albeit, we do not expect any changes in the results presented below).

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with their valence and a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated, and this process was repeated for each of the foundations. Words' percent occurrence were multiplied by their *z*-scored valence. Valences were *z*-scored in order to eliminate any ambiguity regarding the direction of the valence. Positive values indicate positive valence, and negative values indicate negative valence. Words were categorized in accordance to their MFD affiliation, creating a weighted sum for each moral foundation.

```{r stem_text, eval=TRUE, include=FALSE}

final = read.csv("../exp1_data/finaldata.csv", stringsAsFactors = F)
final = na.omit(final) #one weird NA line

##load libraries
library(tm)
library(ngram)

#process the Text column (write a loop) - save processed text as a separate column
for(i in 1:nrow(final)) {

  final$edited[i] = preprocess(final$Text[i], #one value at a time
           case = "lower", 
           remove.punct = TRUE,
           remove.numbers = FALSE, 
           fix.spacing = TRUE)

##stem the words - do this second in the loop
  final$stemmed[i] = stemDocument(final$edited[i], language = "english")
}

```{r stem_warriner, include = FALSE}
##open the Warriner data for later
warriner = read.csv("../exp1_data/BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)

for(i in 1:nrow(warriner)) {
  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
} 
```

```{r create_datasets_harm, echo = F, include=FALSE}
#read in the harm total words from the mtmm project
harm_all = read.csv("../exp1_data/harm_words_total.csv", stringsAsFactors = F)

harm_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
harm_final_data = rbind(harm_final_data, temp2)
}

#pull in the data from Warriner 
harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
#table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn
harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#no spurn avaliable
```

```{r create_datasets_fair, include=FALSE}
fair_all = read.csv("../exp1_data/fair_words_total.csv", stringsAsFactors = F)

fair_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(fair_all$words[fair_all$words != "" & fair_all$words != "NA" & !is.na(fair_all$words)]), ]

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
fair_final_data = rbind(fair_final_data, temp2)
}

fair_final_data$valence = vlookup(fair_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
#just plagiar safer
fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#nothing for just or plagiarism
```

```{r create_datasets_ingroup, include=FALSE}
ingroup_all = read.csv("../exp1_data/ingroup_words_total.csv", stringsAsFactors = F)

ingroup_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & !is.na(ingroup_all$words)]), ]

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
ingroup_final_data = rbind(ingroup_final_data, temp2)
}

ingroup_final_data$valence = vlookup(ingroup_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
#backstabb  benedict      best      fals   indvidu      juda    knight      true
ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
```

```{r create_datasets_authority, include=FALSE}
authority_all = read.csv("../exp1_data/authority_words_total.csv", stringsAsFactors = F)

authority_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(authority_all$words[authority_all$words != "" & authority_all$words != "NA" & !is.na(authority_all$words)]), ]

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
authority_final_data = rbind(authority_final_data, temp2)
}

authority_final_data$valence = vlookup(authority_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
#  abov behind   gase higher  older  taken 
authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
```

```{r create_datasets_purity, include=FALSE}
purity_all = read.csv("../exp1_data/purity_words_total.csv", stringsAsFactors = F)

purity_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(purity_all$words[purity_all$words != "" & purity_all$words != "NA" & !is.na(purity_all$words)]), ]

#control here for times when no words
if (nrow(temp2) == 0){
  temp2 = data.frame("Var1" = 0, "Freq" = 0)
}

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
purity_final_data = rbind(purity_final_data, temp2)
}

purity_final_data$valence = vlookup(purity_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(purity_final_data$Var1[is.na(purity_final_data$valence) & purity_final_data$Freq > 0])
#befor christian     jesus      mari      none    sacred    someon      true     women 
purity_final_data$valence[purity_final_data$Var1 == "sacred"] = warriner$V.Mean.Sum[warriner$Word2 == "sacr"]
purity_final_data$valence[purity_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
purity_final_data$valence[purity_final_data$Var1 == "women"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "woman"])
```

```{r descriptives, echo = F, include = FALSE}
#summarize the dataset so that you have the total and percent for each foundation 
# summary(harm_final_data)
# summary(fair_final_data)
# summary(ingroup_final_data)
# summary(authority_final_data)
# summary(purity_final_data)
# #report descriptive statistics of the foundations
# mean(harm_final_data$valence)
# sd(harm_final_data$valence)
# mean(fair_final_data$valence)
# sd(fair_final_data$valence)
# mean(ingroup_final_data$valence)
# sd(ingroup_final_data$valence)
# mean(authority_final_data$valence)
# sd(authority_final_data$valence)
# mean(purity_final_data$valence)
# sd(purity_final_data$valence)
#note that a big problem is the valence of the words 
```

```{r analysis_harm, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100

#flatten down to sum by article 
harm_final_temp = aggregate(harm_final_data$weight, 
          by = list(harm_final_data$URL),
          FUN = sum, na.rm = T)
colnames(harm_final_temp) = c("URL", "MFDweight")

harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
                       grepl("npr.org", harm_final_temp$URL)] = "Liberal"
harm_final_temp$lean[grepl("breitbart.com", harm_final_temp$URL) |
                       grepl("foxnews.com", harm_final_temp$URL)] = "Conservative"

harm_final_temp$Source[grepl("nytimes.com", harm_final_temp$URL)] = "NY Times"
harm_final_temp$Source[grepl("npr.org", harm_final_temp$URL)] = "NPR"
harm_final_temp$Source[grepl("foxnews.com", harm_final_temp$URL)] = "Fox"
harm_final_temp$Source[grepl("breitbart.com", harm_final_temp$URL)] = "Breitbart"

harm_model = lme(MFDweight ~ lean, 
                 data = harm_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(harm_model)
```

```{r analysis_fair, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
fair_final_data$weight = fair_final_data$Freq * fair_final_data$valence / fair_final_data$wordcount * 100

#flatten down to sum by article 
fair_final_temp = aggregate(fair_final_data$weight, 
          by = list(fair_final_data$URL),
          FUN = sum, na.rm = T)
colnames(fair_final_temp) = c("URL", "MFDweight")

fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
                       grepl("npr.org", fair_final_temp$URL)] = "Liberal"
fair_final_temp$lean[grepl("breitbart.com", fair_final_temp$URL) |
                       grepl("foxnews.com", fair_final_temp$URL)] = "Conservative"

fair_final_temp$Source[grepl("nytimes.com", fair_final_temp$URL)] = "NY Times"
fair_final_temp$Source[grepl("npr.org", fair_final_temp$URL)] = "NPR"
fair_final_temp$Source[grepl("foxnews.com", fair_final_temp$URL)] = "Fox"
fair_final_temp$Source[grepl("breitbart.com", fair_final_temp$URL)] = "Breitbart"

fair_model = lme(MFDweight ~ lean, 
                 data = fair_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(fair_model)
```

```{r analysis_ingroup, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
ingroup_final_data$weight = ingroup_final_data$Freq * ingroup_final_data$valence / ingroup_final_data$wordcount * 100

#flatten down to sum by article 
ingroup_final_temp = aggregate(ingroup_final_data$weight, 
          by = list(ingroup_final_data$URL),
          FUN = sum, na.rm = T)
colnames(ingroup_final_temp) = c("URL", "MFDweight")

ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
                       grepl("npr.org", ingroup_final_temp$URL)] = "Liberal"
ingroup_final_temp$lean[grepl("breitbart.com", ingroup_final_temp$URL) |
                       grepl("foxnews.com", ingroup_final_temp$URL)] = "Conservative"

ingroup_final_temp$Source[grepl("nytimes.com", ingroup_final_temp$URL)] = "NY Times"
ingroup_final_temp$Source[grepl("npr.org", ingroup_final_temp$URL)] = "NPR"
ingroup_final_temp$Source[grepl("foxnews.com", ingroup_final_temp$URL)] = "Fox"
ingroup_final_temp$Source[grepl("breitbart.com", ingroup_final_temp$URL)] = "Breitbart"

ingroup_model = lme(MFDweight ~ lean, 
                 data = ingroup_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(ingroup_model)
```

```{r analysis_authority, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
authority_final_data$weight = authority_final_data$Freq * authority_final_data$valence / authority_final_data$wordcount * 100

#flatten down to sum by article 
authority_final_temp = aggregate(authority_final_data$weight, 
          by = list(authority_final_data$URL),
          FUN = sum, na.rm = T)
colnames(authority_final_temp) = c("URL", "MFDweight")

authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
                       grepl("npr.org", authority_final_temp$URL)] = "Liberal"
authority_final_temp$lean[grepl("breitbart.com", authority_final_temp$URL) |
                       grepl("foxnews.com", authority_final_temp$URL)] = "Conservative"

authority_final_temp$Source[grepl("nytimes.com", authority_final_temp$URL)] = "NY Times"
authority_final_temp$Source[grepl("npr.org", authority_final_temp$URL)] = "NPR"
authority_final_temp$Source[grepl("foxnews.com", authority_final_temp$URL)] = "Fox"
authority_final_temp$Source[grepl("breitbart.com", authority_final_temp$URL)] = "Breitbart"

authority_model = lme(MFDweight ~ lean, 
                 data = authority_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(authority_model)
```

```{r analysis_purity, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
purity_final_data$weight = purity_final_data$Freq * purity_final_data$valence / purity_final_data$wordcount * 100

#flatten down to sum by article 
purity_final_temp = aggregate(purity_final_data$weight, 
          by = list(purity_final_data$URL),
          FUN = sum, na.rm = T)
colnames(purity_final_temp) = c("URL", "MFDweight")

purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
                       grepl("npr.org", purity_final_temp$URL)] = "Liberal"
purity_final_temp$lean[grepl("breitbart.com", purity_final_temp$URL) |
                       grepl("foxnews.com", purity_final_temp$URL)] = "Conservative"

purity_final_temp$Source[grepl("nytimes.com", purity_final_temp$URL)] = "NY Times"
purity_final_temp$Source[grepl("npr.org", purity_final_temp$URL)] = "NPR"
purity_final_temp$Source[grepl("foxnews.com", purity_final_temp$URL)] = "Fox"
purity_final_temp$Source[grepl("breitbart.com", purity_final_temp$URL)] = "Breitbart"

purity_model = lme(MFDweight ~ lean, 
                 data = purity_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(purity_model)
```

# Results

## Descriptive Statistics

```{r exp1-source-descriptives, results = 'asis', echo = FALSE, message = F}

final$uniquewords = NA
final$valenceavg = NA

for (i in 1:nrow(final)){

  #add unique
  final$uniquewords[i] = length(unique(unlist(strsplit(final$stemmed[i], " "))))

  #add valence
  tempwords = as.data.frame(unlist(strsplit(final$stemmed[i], " ")))
  colnames(tempwords) = "theword"
  tempwords$tempval = vlookup(tempwords$theword, #index in original data
                    warriner, #where's the stuff you want to put in
                    "V.Mean.Sum", #what column is the stuff you want
                    "Word2") #what's the matching index

  final$valenceavg[i] = mean(tempwords$tempval, na.rm = T)

# tapply(final$valenceavg, final$Source, mean)
# tapply(final$valenceavg, final$Source, sd)
# tapply(final$wordcount, final$Source, mean)
# tapply(final$wordcount, final$Source, sd)
# tapply(final$uniquewords, final$Source, mean)
# tapply(final$uniquewords, final$Source, sd)
# tapply(final$Source, final$Source, length)
# tapply(final$wordcount, final$Source, sum)

library(quanteda)

final$FK = NA

for (i in 1:nrow(final)){
  final$FK[i] = unlist(textstat_readability(final$Text[i], 
                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
}

# tapply(final$FK, final$Source, mean)
# tapply(final$FK, final$Source, sd)

####build the table here####
tableprint = matrix(NA, nrow=4, ncol=11)
colnames(tableprint) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")

#tableprint[ , 1] = unique(final$Source)
tableprint[ , 1] = c("Breitbart", "Fox News", "NPR", "New York Times")
tableprint[ , 2] = tapply(final$valenceavg, final$Source, mean)
tableprint[ , 3] = tapply(final$valenceavg, final$Source, sd)
tableprint[ , 4] = tapply(final$valenceavg, final$Source, length)
tableprint[ , 5] = tapply(final$wordcount, final$Source, sum)
tableprint[ , 6] = tapply(final$wordcount, final$Source, mean)
tableprint[ , 7] = tapply(final$wordcount, final$Source, sd)
tableprint[ , 8] = tapply(final$uniquewords, final$Source, mean)
tableprint[ , 9] = tapply(final$uniquewords, final$Source, sd)
tableprint[ , 10] = tapply(final$FK, final$Source, mean)
tableprint[ , 11] = tapply(final$FK, final$Source, sd)

tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))

tableprint = tableprint[c(3, 4, 1, 2) , ]

#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6))
          )
```

The researchers calculated descriptive statistics for each news source in order to understand any and all fundamental linguistic differences in the sources' use of English. Statistics calculated included average *z*-scored valence of the unique words per article, number of articles per source, total number of words per source, average number of tokens (words) per article in each source, average number of types (unique words) per article in each source, and mean readability level per source. Readability statistics were calculated using the Flesch-Kincaid Grade Level Readability formula [@Kincaid1975]. Readability is calculated using a formula where the total number of syllables, words, and sentences in a given passage are determinants of its difficulty. The obtained value is intended to match up with the grade level at which one should be able to comfortably read the passage [@Kincaid1975]. For example, a text with a readability score of 11 should be easily read by a high school junior.

As seen in Table \@ref(tab:exp1-source-descriptives), the sources are similar in some aspects yet different in others. Valence appears to be slightly positive across all sources. The large standard deviations seem to indicate little to no presence of a difference in valence across sources. 
*The New York Times* published the greatest number of articles as well as total words. *Breitbart* featured the lowest number of articles, and *NPR* the lowest number of total words from all articles. Per individual article, however, *Breitbart* appears to feature the highest average number of words as well as unique words. Once again the standard deviations call into question any apparent differences between sources. Finally, *Fox News* articles had the lowest reading grade level on average, while *The New York Times* had the highest. This result might be attributable to the greater number of tokens in the average *New York Times* article compared to *Fox News*. The standard deviations for readability suggest the presence of a diverse array of articles for each source, ranging from low to high reading level. Large standard deviations suggest the sources feature a lot of overlap between them in their representation of scores.

## Inferential Statistics

>>>>

---
title: "Web Scraping"
author: "Erin M. Buchanan"
date: "3/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

## Experiment 1 Web Scraping Code

@@

## Experiment 1 Data Analysis

@@

## Experiment 2 Web Scraping Code
